DSSynth: An Automated Controller Synthesis Tool \\ for Physical Plants via MATLAB Toolbox

### 2017-06-06 ase2017/paper.tex
improved labels of Figure 3
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%

\begin{figure}[ht]
    \centering
    \subfloat[Define representation and the physical plant.]{
		\includegraphics[width=0.2\textwidth]{step1.png}
		\label{step1}}
		\hfil
    \subfloat[Determine the implementation and the dynamic range.]{
	\includegraphics[width=0.2\textwidth]{step2.png}
		\label{step2}}
		\hfil
    \subfloat[Digital controler synthesized.]{
	\includegraphics[width=0.2\textwidth]{step3.png}
		\label{step2}}
		\hfil
    \subfloat[Step Response for the stable digital controller synthesized]{
	\includegraphics[width=0.22\textwidth]{step4.png}
		\label{step3}}
		\hfil
    \caption{GUI application for the digital synthesis based on the transfer function representation.}
    \label{fig:gui-for-tf}
\end{figure}

>>>>

A graphical user interface application was developed (Fig.~\ref{fig:gui-for-tf}) 
to favor digital controller synthesis in MATLAB, besides improving usability and, 
consequently, attracting more digital dynamical system engineers. Users can provide all 
required parameters for digital controller synthesis: physical plant specification, 
fixed-point representation and dynamic inputs. 
%
\begin{figure}[ht]
    \centering
    \subfloat[Define the system representation and the physical plant.]{
		\includegraphics[width=0.2\textwidth]{step1.png}
		\label{step1}}
		\hfil
    \subfloat[Define implementation features and dynamic range.]{
	\includegraphics[width=0.2\textwidth]{step2.png}
		\label{step2}}
		\hfil
    \subfloat[Digital controller synthesized by DSSynth.]{
	\includegraphics[width=0.2\textwidth]{step3.png}
		\label{step2}}
		\hfil
    \subfloat[Step Response for the synthesized digital controller]{
	\includegraphics[width=0.22\textwidth]{step4.png}
		\label{step3}}
		\hfil
    \caption{DSSynth GUI application for the controller synthesis based on transfer function representation.}
    \label{fig:gui-for-tf}
\end{figure}
